Reading Notes

### 2020-05-15 paper.tex
fixed mendeley library finally? reading opv review

\cite{Mikhnenko2012}
Exciton diffusion length (EDL) in narrow bangap polymers. photoluminescense decay time is related and measurable. PCBM and PCDTBTs modeled with Monte Carlo--code available. They used P3HT as reference (5.4+/-0.7nm exciton diffusion length). 
Exciton diffusion is essential for organic solar cells. excitons are electron hole pairs created by excitation due to light absorption. they are separated into free charges at an interface which creates current. the movement of the excitons through hopping is what is refered to as diffusion. Exciton diffusion length is a factor in device efficiency.
Other methods to measure EDL are fluorescence quenching - the dependence of the exciton quenching efficiency vs semiconductor thickness is fit to 1D diffusion equation. Pros: direct measuremnt, cons: difficult experimentally and there are many things to consider in the model (FRET, effect of polymer-vaccuum interface, optical interference). 
This paper uses MC to model PL decay.
(Losing focus come back tomorrow)
\cite{Alessandri2017b}
\cite{Scharber2013}
\cite{Scharber2006a}
\cite{Yu1995}
\cite{Halls1995}
\cite{Kim2006}
\cite{Lee2011}
\cite{Huang2010}
\cite{Jankowski2013}
\cite{Marsh2014}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}

>>>>

\cite{Mikhnenko2012}
Exciton diffusion length (EDL) in narrow bangap polymers. photoluminescense decay time is related and measurable. PCBM and PCDTBTs modeled with Monte Carlo--code available. They used P3HT as reference (5.4+/-0.7nm exciton diffusion length). 
Exciton diffusion is essential for organic solar cells. excitons are electron hole pairs created by excitation due to light absorption. they are separated into free charges at an interface which creates current. the movement of the excitons through hopping is what is refered to as diffusion. Exciton diffusion length is a factor in device efficiency.
Other methods to measure EDL are fluorescence quenching - the dependence of the exciton quenching efficiency vs semiconductor thickness is fit to 1D diffusion equation. Pros: direct measuremnt, cons: difficult experimentally and there are many things to consider in the model (FRET, effect of polymer-vaccuum interface, optical interference). 
This paper uses MC to model PL decay.
(Losing focus come back tomorrow)

Ugh. I think I've finally fixed my Mendeley library?
\cite{Scharber2013}
Review of state-of-the-art OPV BHJ solar cells. 
pros: thin/light, semitransparent, cheap, continuous production process, short payback times, easy to integrate into new and existing products. 
History of development from 2001 2.5\% PCE to 2011 10\% PCE. Most degrade when exposed to air and sunlight within a few years. Molecular structure including side chains affects stability. Electron affinity of the acceptor determines degradation rate of the semiconductor. Changing the elctrode and using the inverted design(? read waldauf) helps the electrode oxidation. This requires no vacuum
They discuss BHJ morphology and how the A and D regions need to be small enough that an exciton could find it's way to an interface but not so small that once the charge is separated and current is generated at that interface that the current couldn't get to the electrode. The ideal is an interlocked comb structure but in reality solution processed OPVs form patches. This review is not about morphology (they recommened Hoppe2004). Morphology can only effect the efficiency of an AD pair, not the ultimately efficiency limit. This depends on the bandgap and electron affinities of the DA moeities.
fig 5 explains inverted design a bit. 
They discuss costs and efficiencies. Should probably read about Shockley Queisser Limit. (ref 47) based on analysis of pn solar cell they say the max efficiency is 30\% and the optimum band gap in 1.1 eV. Archer and Bolton roughly confirm this -- much of the light energy is lost because the photon is too small to excite the absorber, other loss is due to intraband thermalization of charge carriers (?), 12\% entropic loss, 1\% radiative recombination. Assumption of the Shockley Queisser limit
1. each absorbed photon generates and e/hole pair
2. perfect charge collection
3. radiative recombination as the only recombination.
Based on this work and the external radiative efficiency (ERE) proposed by Green, and actual max of 15-16\% efficiency is predicted.
(continue from 5)
\cite{Waldauf2006}
Read this with intention of understanding inverted design only
\cite{Hoppe2004}
\cite{Scharber2006a}
\cite{Yu1995}
\cite{Halls1995}
\cite{Kim2006}
\cite{Lee2011}
\cite{Huang2010}
\cite{Jankowski2013}
\cite{Marsh2014}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
\cite{}
